Supplementary Information

### 2020-05-26 doc/manuscript/MEE_manuscript.Rmd
added links to GitHub issues

Climate and environmental driver data were obtained from global databases. Monthly climate data for 1901-20XX was obtained from CRU v.4.0X (Harris et al. 2014, [2020](https://rdcu.be/b3U3e)). Variables considered here included mean, minimum, and maximum temperatures; daily temperture range; precipitation; wet day frequency; cloud cover; and potential evapotranspiration (PET). Atmospheric CO~2~... (**ISSUE: need to download**). Atmospheric deposition... (**ISSUE: need to obtain/ organize**). Analyses were, necessarily, limited ot the time frame over which these were available.

@@

To check that this process identified similar climate variables to what would be identified using traditional methods, ... (**ISSUE: do a standardized analysis similar to Helcoski et al. for each site? or just compare with previous studies for each site?**)
(**ISSUE: check that we get similar results with $\Delta r$ and $\Delta AGB$)

A challenge to this system arose for the site undergoing most rapid climate change: Scotty Creek. 
There, [temperatures have increased by X $^\circ$ over X years]..., resulting in negative growth trends in basal area index (BAI) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees (Sniderhan & Baltzer 2016).
Problematically, correlating tree growth residuals from which climate-driven trends had been removed against the climate signal with a strong directional trend would not necessarily identify the most signficant climate drivers.
(**ISSUE: How do we solve this? Any possibility besides subjectively selecting the drivers? Maybe try analysis without detrending**)

>>>>

Climate and environmental driver data were obtained from global databases. Monthly climate data for 1901-20XX was obtained from CRU v.4.0X (Harris et al. 2014, [2020](https://rdcu.be/b3U3e)). Variables considered here included mean, minimum, and maximum temperatures; daily temperture range; precipitation; wet day frequency; cloud cover; and potential evapotranspiration (PET). Atmospheric CO~2~... (**[ISSUE #16 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/16): obtain data**). Atmospheric deposition... (**[ISSUE #17 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/17): obtain data**). Analyses were, necessarily, limited ot the time frame over which these were available.

@@

To check that this process identified similar climate variables to what would be identified using traditional methods, ... (**[ISSUE #35 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/35): do a standardized analysis similar to Helcoski et al. for each site? or just compare with previous studies for each site?**)
(**[ISSUE #34 in ForestGEO-climate-sensitivity](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/34): check that we get similar results with $\Delta r$ and $\Delta AGB$**)

A challenge to this system arose for the site undergoing most rapid climate change: Scotty Creek. 
There, [temperatures have increased by X $^\circ$ over X years]..., resulting in negative growth trends in basal area index (BAI) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees (Sniderhan & Baltzer 2016).
Problematically, correlating tree growth residuals from which climate-driven trends had been removed against the climate signal with a strong directional trend would not necessarily identify the most signficant climate drivers.
(**[ISSUE #25 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/25): How do we solve this? Any possibility besides subjectively selecting the drivers? Maybe try analysis without detrending**)
